Response to reviewers

### 2022-02-18 response/response1.Rmd
fixed the reviewer comment on censoring
satisfied all of the NEED HELP

* We thank the reviewer for pointing out to us that the data contains information on the work experience -- this additional data is added in the extraction of the data in Figure 1. We also add a Subsection dedicated to explain this variable, i.e., Subsection 3.2. Calculated variables: work experience. This information was compared with Singer & Willet's original data. Comparison shown in Figure 7 shows that the information does not match up, however, there is a high correlation between the variables.

* **NEED HELP in responding comments on Figure 8.**

@@

* We have made the descriptions of the steps more explicit as follows [LIST OF THE CHANGES]

@@

* **NEED HELP** The paper has been fixed so that male/female is used consistently. We have also rewritten the paragraph to focus on the survey questions and shortcomings.

@@

* **NEED HELP**

@@

* **NEED HELP** Figure 8 has been updated, and other comparisons of the original and refreshed data have been added. There are still some differences, but with the change in variables being created and better filtering to get the dropouts the data are now more similar.

@@

* NEED HELP We are really not sure what this refers to.

>>>>

* We thank the reviewer for pointing out to us that the data contains information on the work experience -- this additional data is added in the extraction of the data in Figure 1. We also add a Subsection dedicated to explain this variable, i.e., Subsection 3.2. Calculated variables: work experience. This information was compared with Singer & Willet's original data. Comparison between the subsets has been completely revised.

@@

@@

* The paper has been fixed so that male/female is used consistently. We have also rewritten the paragraph to focus on the survey questions and shortcomings.

@@

* Added some additional text on this.

@@

* The comparison of the original and refreshed data has been completely rewritten. There are still some differences, but with the change in variables being created and better filtering to get the dropouts the subsets are now more similar.

@@

* We are really not sure what this refers to. Perhaps it is solved with the revisions.
